Local Spectral Clustering of Density Upper Level Sets

### 2019-05-01 arxiv/arxiv_local_density_clustering.tex
finalized examples, added partial redraft of proofs for ppr section

	\begin{subfigure}{.33\linewidth}
		\includegraphics[width=\linewidth]{example1plots/sigma_mixing_time_plot}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.33\linewidth}
		\includegraphics[width=\linewidth]{example1plots/diameter_normalized_cut_plot}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.33\linewidth}
		\includegraphics[width=\linewidth]{example1plots/diameter_mixing_time_plot}
		\caption{}
	\end{subfigure}
	\end{adjustbox}
\end{figure}

@@

To form each of the four rows in Figure \ref{fig:fig2}, 800 points are independently sampled following a 'two moons plus Gaussian noise model'. Formally, the (respective) generative models for the data are
\begin{align}
Z & \sim \textrm{Bern}(1/2), \theta \sim \textrm{Unif}(0, \pi) \\
X(Z,\theta) & = 
\begin{cases}
\mu_1 + (r \cos(\theta), r \sin(\theta)) + \sigma \epsilon,~ & \text{if}~ Z = 1 \\
\mu_2 + (r \cos(\theta), - r \sin(\theta)) + \sigma \epsilon,~ & \text{if}~ Z = 0
\end{cases}
\end{align}

>>>>

	\begin{subfigure}{.33\linewidth}
		\includegraphics[width=\linewidth]{example1plots/sigma_mixing_time_plot}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.33\linewidth}
		\includegraphics[width=\linewidth]{example1plots/diameter_normalized_cut_plot}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.33\linewidth}
		\includegraphics[width=\linewidth]{example1plots/diameter_mixing_time_plot}
		\caption{}
	\end{subfigure}
	\caption{}
	\label{fig:fig1}
	\end{adjustbox}
\end{figure}

As we do not provide any theoretical lower bounds, we validate the tightness of Theorems \ref{thm: conductance_upper_bound} and \ref{thm: inverse_mixing_time_lower_bound} via simulation.  We sample points according to the density function $q$, where for $x \in \Rd$
\begin{equation}
q(x) :=
\begin{cases}
\lambda,~ & x \in [0,\sigma] \times D^{d-1} =: \Cset, \\
\lambda - \dist(x,\Cset)\eta,~ & x \in \Csig \setminus \Cset, \\
(\lambda - \sigma \eta) - \dist(x,\Csig)^{\gamma}, & x \in (\Csig + \sigma B), \setminus \Csig \\
0,~ & \textrm{otherwise},
\end{cases}
\end{equation}
where $\lambda = \frac{150}{81} \sigma^{\gamma}$ and $\eta = \frac{15}{81} \sigma^{\gamma - 1}$. Panels $(a)$ and $(b)$ in Figure \ref{fig:fig1} show $20,000$ samples from two parameterizations of $q$. In $(a)$, $\sigma = D = 3.2$, while in $(b)$ $\sigma = .1$ and $D = 3.2$. (For both, $d = 2$).

Panels $(c) - (f)$ in Figure \ref{fig:fig1} show the change in normalized cut and mixing time, respectively, as the parameters $\sigma$ ($(c)$ and $(d)$) and $D$ ($(e)$ and $(f)$) are varied. In panels $(c)$ and $(d)$ $\sigma = .1 \cdot \sqrt{2}^j, j = 1,\ldots,10$, and $D$ is fixed at $3.2$. In panels $(e)$ and $(f)$, $D = .1 \cdot \sqrt{2}^j, j = 1,\ldots,10$ and $\sigma$ is fixed at $.1$.
For each panel, the solid lines show, up to constants \footnote{Note that we have rescaled all values of theoretical upper bounds by a constant, in order to mask the effect of large universal constants in these bounds. Therefore only comparison of slopes, rather than intercepts, is meaningful.}, the theoretical upper bound, given by Theorem \ref{thm: conductance_upper_bound} for panels $(c)$ and $(e)$ and Theorem \ref{thm: inverse_mixing_time_lower_bound} for panels $(d)$ and $(f)$. The dashed lines show the computed empirical value, averaged over $m$ trials ($m = 100$ for the normalized cut, dashed lines in panels $(c)$ and $(e)$, and $m = 20$ for the mixing time, dashed lines in panel $(d)$ and $(f)$). For each trial across all parameters, $r$, the neighborhood graph radius, is set throughout to be as small as possible such that the resulting graph is connected, for computational efficiency. Green lines correspond to dimension $d = 2$, whereas purple/pink lines correspond to $d = 3$.

Panels $(d)$ and $(f)$ show the solid lines tracking closely to the dashed lines, in both 2 and 3 dimensions. This provides empirical evidence that the upper bound on mixing time given by Theorem \ref{thm: inverse_mixing_time_lower_bound} has the right dependency on both thickness parameter  $\sigma$ and diameter $D$.

\textcolor{red}{The story in panels $(c)$ and $(e)$ is more subtle. We note that while, broadly speaking, the trends do not appear to match, this gap between theory and empirical results is mostly due to the relationship when $\sigma \approx D$; this is the right hand side on panel $(c)$ and the left hand side on panel $(e)$. It is in these regions that the slopes of the dashed and solid lines appear most distinct. As the ratio $D/\sigma$ grows, we see the slopes of the empirical curves converging towards those predicted by theory. The takeaway message is that while the dependency in \eqref{eqn: conductance_additive_error_bound} on $\sigma$ and $D$ is loose for clusters with diameter close to thickness, it becomes tighter and tigher as $D/\sigma$ grows.}

@@

To drive home the main implications of Theorem \ref{thm: ppr_cluster}, we show the behavior of \pprspace, normalized cut, and the density clustering algorithm of \citep{chaudhuri2010} on (a variant of) the famous 'two moons' dataset, considered a prototypical success story for spectral clustering algorithms. To form each of the four rows in Figure \ref{fig:fig2}, 800 points are independently sampled following a 'two moons plus Gaussian noise model'. Formally, the (respective) generative models for the data are
\begin{align}
Z & \sim \textrm{Bern}(1/2), \theta \sim \textrm{Unif}(0, \pi) \\
X(Z,\theta) & = 
\begin{cases}
\mu_1 + (r \cos(\theta), r \sin(\theta)) + \sigma \epsilon,~ & \text{if}~ Z = 1 \\
\mu_2 + (r \cos(\theta), - r \sin(\theta)) + \sigma \epsilon,~ & \text{if}~ Z = 0
\end{cases}
\end{align}

### 2019-05-01 arxiv/arxiv_local_density_clustering_proofs.tex
finalized examples, added partial redraft of proofs for ppr section

Let $\pbf = (p_u)_{u \in \Xbf}$ denote the \pprspace vector computed over $G_{n,r}$ (where for ease of reading we suppress dependence on the hyperparameter $\alpha$ and seed node $v$.) 
Recalling that $\widetilde{\pi}_{n,r}$ is the stationary distribution over $\widetilde{G}_{n,r}$, we write $\widetilde{\pi}_{n,r}(u)$ to denote the stationary distribution evaluated at $u \in \Csig[X]$.

@@

Lemma \ref{lem: setup} formalizes the intuitively sensible statement that \pprspace, can be uniformly lower bounded over clusters with small mixing time relative to their normalized cut. Importantly, it adds a corresponding upper bound for \pprspace outside of these clusters.
\begin{lemma} 
	\label{lem: setup}
	Consider running Algorithm \ref{alg: ppr} with any $r < \sigma$ and

	\begin{equation} 
	\label{eqn: upper_bound_alpha}
	\frac{\Psi_{n,r}(\Csig[\Xbf])}{10} \leq \alpha \leq \frac{\Psi_{n,r}(\Csig[\Xbf])}{9}.
	\end{equation}

	There exists a good set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ with $\vol(\Csig[\Xbf]^g) \geq \vol(\Csig[\Xbf])/2$ such that the following statements hold for all $v \in \Csig[\Xbf]^g$:
	\begin{itemize}
		\item For all $u \in \Cset[\Xbf]$,
		\begin{equation}
		\label{eqn: lower_bound_PPR_in_cluster}
		p_u \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u) - \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \widetilde{D}_{\min}}
		\end{equation}
		\item For all $u' \in \Csig'[\Xbf]$,
		\begin{equation}
		\label{eqn: upper_bound_PPR_in_other_cluster}
		p_{u'} \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \widetilde{D}_{\min}}
		\end{equation}
	\end{itemize}
\end{lemma}

@@

	We introduce \emph{leakage} and \emph{soakage} vectors, defined by
	\begin{align*}
	\ell_t & := e_v (\Wbf_n \widetilde{\mathbf{I}}_n )^t (\mathbf{I}_n - \Dbf_n^{-1} \wDbf_{n}) \\
	\ell & := \sum_{t = 0}^{\infty} (1 - \alpha)^t \ell_t \\
	s_t & := e_v (\Wbf_n \widetilde{\mathbf{I}}_n )^t (\Wbf_n \widetilde{\mathbf{I}}_n^c) \\
	s & := \sum_{t = 0}^{\infty} (1 - \alpha)^{t} s_t
	\end{align*}
	where $\mathbf{I}_n$ is the $n \times n$ identity matrix, $\widetilde{\mathbf{I}}_n$ is a diagonal matrix with $(\widetilde{\mathbf{I}}_n)_{uu} = 1$ if $u \in \Csig[\Xbf]$ and $\widetilde{\mathbf{I}}_n^c = \mathbf{I}_n - \widetilde{\mathbf{I}}_n$.

	Roughly, the proof will unfold in four steps. The first two will result in the lower bound of (\ref{eqn: lower_bound_PPR_in_cluster}), while the latter two will imply the upper bound in (\ref{eqn: upper_bound_PPR_in_other_cluster}).

	\begin{enumerate}
		\item For $u \in \Cset'[\Xbf]$, use the results of \cite{zhu2013} to produce the lower bound 
		\begin{equation*}
		\pbf(u) \geq 4/5 \widetilde{\pi}_{n,r}(u) - \widetilde{\pbf}_{\ell}(u)
		\end{equation*}
		where 
		\begin{equation*}
		\widetilde{\pbf}_{\ell} = \alpha \ell + (1 - \alpha) \widetilde{\pbf}_{\ell} \widetilde{\Wbf}_n
		\end{equation*}
		is the \pprspace random walk over $\widetilde{G}_{n,r}$, and $\ell$ has bounded norm $||\ell||_1 \leq 2\frac{\Phi_{n,r}(\Csig[\Xbf])}{\alpha}$.

		\item Since $r < \sigma$, for any $u \in \Cset[\Xbf]$ there are no edges between $u$ and $G_{n,r} / \Csig[\Xbf]$. Therefore, the page-rank vector $\widetilde{\pbf}_{\ell}$ will not assign more than $||\ell||_1 / d_{\min}(\Csig[\Xbf])$ probability mass to any vertex in $\Cset'[\Xbf]$. This observation will conclude our proof of (\ref{eqn: lower_bound_PPR_in_cluster}).
		\item For vertices $u' \in G_{n,r} / \Csig[\Xbf]$, we can upper bound $p_v(u) \leq p_s(u')$. In particular, this hold for all $u' \in \Cset'[\Xbf]$.
		\item Since $r < \sigma$, there are no edges between $u'$ and $G / \Cset'[\Xbf]$. Therefore, the page-rank vector $p_{s}$ will assign no more than $||s||_1 / d_{\min}(\Csig[\Xbf])$ probability mass to any vertex in $\Cset'[\Xbf]$. Additionally, $s$ has bounded norm $||s||_1 \leq ||\ell||_1$. This will conclude our proof of (\ref{eqn: upper_bound_PPR_in_other_cluster}), and hence Lemma \ref{lem: setup}.
	\end{enumerate}

>>>>

@@

Recall that for teleportation parameter $\alpha  \in (0,1]$ and seed node $v \in \Xbf$, we write $\pbf(v, \alpha; G_{n,r})$ for the \pprspace vector computed over neighborhood graph $G_{n,r}$; let $\pbf(u)$ denote the entry of $\pbf(v, \alpha; G_{n,r})$ at vertex $u \in \Xbf$. 
Recalling that we write $\widetilde{\pibf}_{n,r}$ for the stationary distribution over $\widetilde{G}_{n,r}$, write $\widetilde{\pibf}_{n,r}(u)$ denote the stationary distribution at vertex $u \in \Csig[\Xbf]$.

Lemma \ref{lem: setup} states the key results needed to link Theorems \ref{thm: conductance_upper_bound} and \ref{thm: inverse_mixing_time_lower_bound} with Theorem \ref{thm: consistent_recovery_of_density_clusters}.  
\begin{lemma} 
	\label{lem: setup}
	Let $0 < r < \sigma$ and
	\begin{equation} 
	\label{eqn: upper_bound_alpha}
	\frac{\Psi_{n,r}(\Csig[\Xbf])}{10} \leq \alpha \leq \frac{\Psi_{n,r}(\Csig[\Xbf])}{9}.
	\end{equation}

	There exists a good set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ with $\vol(\Csig[\Xbf]^g; G_{n,r}) \geq \vol(\Csig[\Xbf]; G_{n,r})/2$ such that the following statements hold with respect to $\pbf(v,\alpha;G_{n,r})$ for any $v \in \Csig[\Xbf]^g$:
	\begin{itemize}
		\item For each $u \in \Cset[\Xbf]$,
		\begin{equation}
		\label{eqn: lower_bound_PPR_in_cluster}
		\pbf(u) \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u) - \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \widetilde{D}_{\min}}
		\end{equation}
		\item For any $\Cset' \in \Cbb_f(\lambda)$ such that $\Cset' \neq \Cset$, and for each $u' \in \Csig'[\Xbf]$,
		\begin{equation}
		\label{eqn: upper_bound_PPR_in_other_cluster}
		\pbf(u') \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \widetilde{D}_{\min}}
		\end{equation}
	\end{itemize}
\end{lemma}

\begin{proof}
	The proof of Lemma \ref{lem: setup} is lengthy, but not difficult. We begin with some notation. Recall that $\Wbf_n = \Dbf_n \Abf_n^{-1}$ is the transition probability matrix over $G_{n,r}$. Let $\widetilde{\Dbf}_n$ and $\widetilde{\Wbf}_n$ be the degree and random walk matrices for the subgraph $\widetilde{G}_{n,r}$. Then, given $q \in \Reals^{\Csig[\Xbf]}$ we let
	\begin{equation}
	\widetilde{\pbf}_q = \alpha q + (1 - \alpha) \widetilde{\pbf}_{q} \widetilde{\Wbf}_n 
	\end{equation}
	be the \pprspace vector originating from $q$ over $\widetilde{G}_{n,r}$. (When the starting distribution $q = e_v$ is a point mass at a seed node $v \in \Csig[\Xbf]$, we write $\widetilde{\pbf}_v$ for $\widetilde{\pbf}_{e_v}$ in a slight abuse of notation).

	Our analysis will involve \emph{leakage} and \emph{soakage} vectors, defined by
	\begin{align*}
	\ell_t & := e_v (\Wbf_n \widetilde{\mathbf{I}}_n )^t (\mathbf{I}_n - \Dbf_n^{-1} \wDbf_{n}),~ \ell := \sum_{t = 0}^{\infty} (1 - \alpha)^t \ell_t, \\
	s_t & := e_v (\Wbf_n \widetilde{\mathbf{I}}_n )^t (\Wbf_n \widetilde{\mathbf{I}}_n^c),~ s := \sum_{t = 0}^{\infty} (1 - \alpha)^{t} s_t.
	\end{align*}
	where $\mathbf{I}_n$ is the $n \times n$ identity matrix, $\widetilde{\mathbf{I}}_n$ is an $n \times n$ diagonal matrix with $(\widetilde{\mathbf{I}}_n)_{uu} = 1$ if $u \in \Csig[\Xbf]$ and $0$ otherwise, and $\widetilde{\mathbf{I}}_n^c = \mathbf{I}_n - \widetilde{\mathbf{I}}_n$.

	In words, for $u \in \Csig[\Xbf]$, $\ell_t(u)$ is the probability that a random walk originating from $v$ stays within $\Csig[\Xbf]$ for $t$ steps, arriving at the $t$th step at $u$, and then leaks out of $\Csig[\Xbf]$ on the $t + 1$th step. For $w \not\in \Csig[\Xbf]$, $s_t(w) = 0$. By contrast, $s_t(w)$ is the probability that a random walk originating from $v$ stays within $\Csig[\Xbf]$ for $t$ steps, and then moves to $w$ on the $t + 1$ step, while $s_t(u) = 0$ for all $u \in \Csig[\Xbf]$. The vectors $\ell$ and $s$ then clearly have the same interpretation, but with respect to the total mass leaked and soaked by the \pprspace vector.

	We first prove \eqref{eqn: lower_bound_PPR_in_cluster}, and begin by restating some results of \citep{zhu2013}, adapted to our notation. By Lemma 3.1 of \citep{zhu2013}, there exists a good set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ with $\vol(\Csig[\Xbf]^g; G_{n,r}) \geq \vol(\Csig[\Xbf]; G_{n,r})/2$ such that for every $v \in \Csig[\Xbf]^g$
	\begin{equation}
	\label{eqn: zhulemma3.1}
	\pbf(u) \geq \widetilde{\pbf}_v(u) - \widetilde{\pbf}_{\ell}(u),~ \textrm{and}~ \norm{\ell}_1 \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha}.
	\end{equation}

	If moreover $\alpha \leq \frac{\Psi_{n,r}(\Csig[\Xbf])}{9}$, then additionally by Corollary 3.3 of \citep{zhu2013}, for every $u \in \Csig[\Xbf]$
	\begin{equation*}
	\widetilde{\pbf}(u) \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u)
	\end{equation*}
	and along with \eqref{eqn: zhulemma3.1}, we obtain
	\begin{equation*}
	\pbf(u) \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u) - \widetilde{\pbf}_{\ell}(u).
	\end{equation*}

	We proceed to upper bound $\widetilde{\pbf}_{\ell}(u) \leq \norm{\ell}_1 / \widetilde{D}_{\min}$, whence \eqref{eqn: lower_bound_PPR_in_cluster} follows by \eqref{eqn: zhulemma3.1}. We observe two facts regarding $\widetilde{\pbf}_{\ell}(u)$. First, for any $u \in \Cset$, since $r < \sigma$, $(u,w) \not\in G_{n,r}$ for any $w \not\in \Csig$. As a result, for all $t \geq 1$, $\ell_t(u) = 0$ and by extension, $\ell(u) = 0$ as well.

	Second, for any $q \in \Reals^{\Csig[\Xbf]}$ with $\sum_{w \in \Csig[\Xbf]} q(w) = 1$, and any $t \geq 1$,
	\begin{align*}
	q \widetilde{\Wbf}_n^t (u) & \leq \norm{q}_1 ||\widetilde{\Wbf}_{\cdot u}||_{\infty} \\
	& \leq \frac{1}{\widetilde{D}_{\min}}
	\end{align*}
	where $\widetilde{\Wbf}_{\cdot u}$ is the $u$th column of $\widetilde{\Wbf}$, and the last inequality follows from the fact $(u,w) \in \widetilde{G}_{n,r}$ implies $w \in \Csig$, and therefore
	\begin{equation*}
	\deg(w; \widetilde{G}_{n,r}) \geq \widetilde{D}_{\min}.
	\end{equation*}

	These facts, along with some basic algebra, lead to the desired lower bound on $\widetilde{\pbf}_{\ell}(u)$ for every $u \in \Cset[\Xbf]$:
	\begin{align*}
	\widetilde{\pbf}_{\ell}(u) & = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\ell \widetilde{\Wbf}_n^t \right)(u)  \nonumber \\
	& = \norm{\ell}_1 \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\frac{\ell}{\norm{\ell}_1}  \widetilde{\Wbf}_n^t \right)(u)\nonumber \\
	& = \norm{\ell}_1 \alpha \sum_{t = 1}^{\infty} (1 - \alpha)^t \left(\frac{\ell}{\norm{\ell}_1}  \widetilde{\Wbf}_n^t \right)(u)\nonumber \\
	& \leq \norm{\ell}_1 \frac{1}{\widetilde{D}_{\min}}.
	\end{align*}
	and \eqref{eqn: lower_bound_PPR_in_cluster} is proved.

\subsection{Proof of Lemma \ref{lem: setup}}

@@

	We introduce \emph{leakage} and \emph{soakage} vectors, defined by
	\begin{align*}
	\ell_t & := e_v (\Wbf_n \widetilde{\mathbf{I}}_n )^t (\mathbf{I}_n - \Dbf_n^{-1} \wDbf_{n}),~ \ell := \sum_{t = 0}^{\infty} (1 - \alpha)^t \ell_t, \\
	s_t & := e_v (\Wbf_n \widetilde{\mathbf{I}}_n )^t (\Wbf_n \widetilde{\mathbf{I}}_n^c),~ s := \sum_{t = 0}^{\infty} (1 - \alpha)^{t} s_t.
	\end{align*}
	where $\mathbf{I}_n$ is the $n \times n$ identity matrix, $\widetilde{\mathbf{I}}_n$ is an $n \times n$ diagonal matrix with $(\widetilde{\mathbf{I}}_n)_{uu} = 1$ if $u \in \Csig[\Xbf]$ and $0$ otherwise, and $\widetilde{\mathbf{I}}_n^c = \mathbf{I}_n - \widetilde{\mathbf{I}}_n$.

	Roughly, the proof of Lemma \ref{lem: setup} will unfold in four steps. The first two will result in the lower bound of (\ref{eqn: lower_bound_PPR_in_cluster}), while the latter two will imply the upper bound in (\ref{eqn: upper_bound_PPR_in_other_cluster}). We briefly summarize the approach before diving into the formal proof:

	\begin{enumerate}
		\item For $u \in \Cset[\Xbf]$, we use the results of \cite{zhu2013} to produce the lower bound 
		\begin{equation*}
		\pbf(u) \geq \frac{4}{5}\widetilde{\pi}_{n,r}(u) - \widetilde{\pbf}_{\ell}(u)
		\end{equation*}
		where 
		\begin{equation*}
		\widetilde{\pbf}_{\ell} = \alpha \ell + (1 - \alpha) \widetilde{\pbf}_{\ell} \widetilde{\Wbf}_n
		\end{equation*}
		is the \pprspace random walk over $\widetilde{G}_{n,r}$, and $\ell$ has bounded norm $||\ell||_1 \leq 2\frac{\Phi_{n,r}(\Csig[\Xbf])}{\alpha}$.

		\item Since $r < \sigma$, for any $u \in \Cset[\Xbf]$ there are no edges between $u$ and $\Xbf \setminus \Csig[\Xbf]$. Therefore, the page-rank vector $\widetilde{\pbf}_{\ell}$ will not assign more than $||\ell||_1 / d_{\min}(\Csig[\Xbf])$ probability mass to any vertex in $\Cset'[\Xbf]$. This observation will conclude our proof of (\ref{eqn: lower_bound_PPR_in_cluster}).
		\item For vertices $u' \in G_{n,r} / \Csig[\Xbf]$, we can upper bound $p_v(u) \leq p_s(u')$. In particular, this hold for all $u' \in \Cset'[\Xbf]$.
		\item Since $r < \sigma$, there are no edges between $u'$ and $G / \Cset'[\Xbf]$. Therefore, the page-rank vector $p_{s}$ will assign no more than $||s||_1 / d_{\min}(\Csig[\Xbf])$ probability mass to any vertex in $\Cset'[\Xbf]$. Additionally, $s$ has bounded norm $||s||_1 \leq ||\ell||_1$. This will conclude our proof of (\ref{eqn: upper_bound_PPR_in_other_cluster}), and hence Lemma \ref{lem: setup}.
	\end{enumerate}
